\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\skillItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItem}[1]{
  \item\small{
    \textbf{#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubItem}[1]{
  \item[-]\small{
    \textsl{#1\vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubItemListStart}{\begin{enumerate}}
\newcommand{\resumeSubItemListEnd}{\end{enumerate}\vspace{6pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Ximin Ma} \\
  \textbf Senior Software Engineer \\
  \textbf Mobile: +65 84249472 & Email : \href{mailto:maxmalex1990@gmail.com}{maxmalex1990@gmail.com}\\
  \textbf Github: \href{https://github.com/alex404A}{https://github.com/alex404A}\\
\end{tabular*}

%-----------Introduction-----------------
\section{Introduction}
An experienced full stack engineer, who focuses on backend and is capable of developing from end to end.

A person with team spirit, who leads a team of 9 developers to consistently deliver high quality software.

A curious programmer, who never limits himself in specific language or technology. To be a software engineer first, to be an engineer in specific domain later. 


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tsinghua University}{Beijing, China}
      {Master of Precision Instrument}{Aug. 2012 -- June. 2015}
    \resumeSubheading
      {Tsinghua University}{Beijing, China}
      {Bachelor of Precision Instrument}{Aug. 2008 -- June. 2012}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {6Etates}{Singapore}
      {Senior Software Engineer}{Feb 2017 - Present}
      \resumeItemListStart
        \resumeItem{Fullstack Team Infrastructure}
        \resumeSubItemListStart
          \resumeSubItem{Promote Kubernetes and Docker, introduce code style and code review guideline in team}
          \resumeSubItem{Lead 9 team members for one year as fullstack team leader}
          \resumeSubItem{Lint Tools, Gitlab CI, Spinnaker, Docker, Kubernetes}
        \resumeSubItemListEnd
        \resumeItem{Trade Finance Automize Platform}
        \resumeSubItemListStart
          \resumeSubItem{A solution for trade docs review process, including doc management, info extraction and standard rule check}
          \resumeSubItem{A web app, which integrates ocr/mrc service in workflow. A rule engine, which is a mini javascript interpreter and provides a graphic configuration UI for non-developer user using Blockly}
          \resumeSubItem{Lead 5 team members to develop from scratch for nearly a year as fullstack team leader}
          \resumeSubItem{Dashboard(Java 11/Spring Boot 2), Frontend(Vue.js), Rule Engine(Typescript), Database(Mongodb)}
        \resumeSubItemListEnd
        \resumeItem{Distributed Crawler System}
        \resumeSubItemListStart
          \resumeSubItem{A platform to crawl public data automatically based on configured templates in both web and mobile platform}
          \resumeSubItem{Generate 2 million messages per day. A task server dispatches tasks to distributed clients in three countries. A template engine, which provides a way to evaluate downloaded pages based on mannually configured xml template. A proxy server, which proxies requests sent from mobile platform}
          \resumeSubItem{Cooperate with 2 team members to develop from scratch for nearly 2 years on web platform, and develop mobile platform as team leader for half a year}
          \resumeSubItem{Server(Java 8/Spring MVC/PhantomJS), Client(Python 2/Node.js/Appium/Selenium), Template Engine(Java 8), Proxy Server(Node.js), DataBase(Mysql, Mongodb, Redis, Kafka)}
        \resumeSubItemListEnd
      \resumeItemListEnd
      
    \resumeSubheading
      {National University of Singapore}{Singapore}
      {Assistant Engineer}{Feb 2016 - Jan 2017}
      \resumeItemListStart
        \resumeItem{Algorithm Integration and Data Management Platform}
        \resumeSubItemListStart
          \resumeSubItem{Integrate NLP algorithms in system, and provide a mechanism to call api according to predefined rules for different users. Build a web app to help researchers upload/manage/download data}
          \resumeSubItem{owner of algorithm platform, develop frontend for data management web app}
          \resumeSubItem{Java 7, Angular.js}
        \resumeSubItemListEnd
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------Skills-----------------
\section{Skills}
  \resumeSubHeadingListStart
    \skillItem{Languages}
      {Java, Javascript, Typescript, Python, Golang, Shell}
    \skillItem{Database}
      {Mysql, Mongodb, Redis, Kafka, Elastic Search}
    \skillItem{Others}
      {Git, Docker, Kubernetes, Vim}
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
